Current and future constraints on primordial magnetic fields

### 2017-06-13 pmf.tex
chang's comment

\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
\be \label{eqn:betascaling}
\apmf^{tens} \propto \beta^{1.9},
\ee
to an excellent approximation. 
We use this $\beta$ power law form to handle the PMF timing dependence. }

>>>>

\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent approximation. 
We use this $\beta$ power law form to handle the PMF timing dependence. 
Thus the tensor PMF power will scale as:
\be \label{eqn:betascaling}
\apmf^{tens} \propto  \bpmf^4 \beta^{1.9},
\ee
}
